\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-10-15 redaction/JEGeo/revision_JEGeo/referees/answers/Answer_referee2.tex

\textbf{Our answer:} We devoted a lot of thought to this point, which directly echoed a similar concern by the other referee. The latter writes: ``\emph{Does this observation revise our understanding of say the gains from trade? Does it shed new light on a puzzle many people are thinking about?
One crude suggestion is to see how the reduction in the industry-specific cost terms is related to the industry-level trade elasticities. If the composition effects favor low-elasticity industries, the findings in the paper may have first-order implications for the gains from trade. Another suggestion is to dig deeper into the relative rate at which additive and multiplicative transport costs have declined over time. Since additive transport costs favor rich (high-quality exporting) countries, the disproportionally greater reduction in additive costs can perhaps explain the rise of low-income exporter as documented by Hanson (2012, JEP).}''

All in all, your suggestions and those of the other referees pointed in two directions for the ``Big Picture'' implications of our exercise: either exploring the compositional country-product dynamics underlying of our results, or focusing on the implications regarding grains from trade. Both paths were undeniably worth exploring, but could not be followed in a single paper. Therefore, we decided to focus on the second path, i.e. to  offer insights on the welfare implications of our results. In this regard, the new Section 5 ``The role of additive cost: Theoretical insights'' is devoted to a theory-based analysis of the alterations to welfare gains involved by the relative variations of additive and multiplicative transport costs over our period of analysis.

Our choice to dig into the welfare implications of our results has two main motivations. Firstly, even if ``\emph{the fact that transport costs are both specific and ad-valorem is well known}'', some recent literature still debates the practical importance of additive costs - for example, \cite{Lashkaripour_JIE2020} recently finds (though in a different theoretical setting) support for the iceberg trade cost assumption, i.e, iceberg accounting for almost all trade costs. Secondly, the implications of additive costs have not been fully exhausted in \citet{Irrazabal_2015}, \cite{Hornok-et-al-RES-2015, Hornok-et-al-JIE-2015}, \cite{Alessandria-et-al-AER-2010} or \citet{sorensen2014}. \cite{Kropf-Saure-JIE-2016} estimate the size and shape of per-shipment costs based on Swiss data. \cite{Alessandria-et-al-AER-2010} and \cite{Hornok-et-al-RES-2015} point out the role of per-shipment costs in generating ``lumpiness'' in international trade transactions. \cite{Hornok-et-al-JIE-2015} focus on administrative costs incurring with every shipment (i.e., additive by nature), and draw welfare conclusions regarding the variations of these costs. We complement these various outcome by providing a long-run characterization of both additive and multiplicative component of transports costs. Furthermore we make use of our empirical results to investigate the welfare consequences of the reduction in international transport costs observed over 1974-2019, contrasting two cases: when this reduction is achieved through a combined reduction in the ad-valorem and the additive components (as quantified by our empirical model) or solely through the ad-valorem cost (as standardly modelled in New Trade theoretical approaches). In this regard, we shed light on the welfare variations induced by the ``hyper-globalization'' period (and the subsequent retrenchment after 2008-2009), as well as the disproportionate part of additive transport costs in determining those welfare variations.

To this aim, we embed additive costs in the canonical \citet{melitz} model. More specifically, we start from the canonical \cites{melitz} model where we add additive trade costs. The inclusion of additive costs in a \citet{melitz} setting has already been performed in \citet{sorensen2014} and \citet{Irrazabal_2015}. However, \citet{sorensen2014} exclusively performs a theoretical analysis, without any quantitative exercise. In addition to a partial equilibrium extension of \citet{melitz}, \citet{Irrazabal_2015} do perform a quantitative simulation to assess the welfare variations induced by the presence of additive costs, but the latter is based on a calibration for transport costs restricted to 2004, based on the case of Nowrway. In contrast, our own exercise relies on a several decades time span for the US, allowing us to highlight the welfare alterations induced over time by the relative dynamics of additive and multiplicative costs, based on ``true'' values for the latter - remember that our methodology allows for the identification of both multiplicative and additive costs as a share of total costs, whereas additive costs in \citet{Irrazabal_2015} are expressed relatively to the (median) export price.

### 2021-10-17 redaction/JEGeo/revision_JEGeo/revised_article/DHP_JoEG_rev1.tex
Nouveau graphique et tableau comparaison 10/3
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: Robustness to aggregation} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10_reshaped.tex}
	\begin{tablenotes}
		\scriptsize
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
        \item Transport costs expressed in \% of the fas price (except for $\widehat{t}$ expressed in USD.
		%\item \textbf{Model (A): With ad-valorem transport costs only}
		\item Model (B): With additive and ad-valorem transport costs
	\end{tablenotes}
\end{table}

\begin{figure}[htbp]
	\caption{Transport cost time trends: Robustness to aggregation}
	\label{fig:robustness_to_agregation}
	\begin{center}
		\includegraphics[height=8cm]{scatter_chronology_baseline_baseline10.png}
	\end{center}
\end{figure}

>>>>

\begin{table}[htbp]
	\centering
	\caption{Transport costs estimates: Robustness to aggregation (2005-2019)} \vspace{5mm} \label{tab:baseline10}
	\input{Table_baseline10.tex}
	\input{Table_baseline10_reshaped.tex}
	\begin{tablenotes}
		\scriptsize
		\item Statistics for 1997-1999 and 2002-2019
		\item Statistics are obtained weighting each observation by its value relative to total trade flows.
        \item Transport costs expressed in \% of the fas price (except for $\widehat{t}$ expressed in USD.
		%\item \textbf{Model (A): With ad-valorem transport costs only}
		\item Model (B): With additive and ad-valorem transport costs
	\end{tablenotes}
\end{table}

\begin{figure}[htbp]
	\caption{Transport cost time trends: Robustness to aggregation (2005-2019)}
	\label{fig:robustness_to_agregation}
	\begin{center}
		\includegraphics[height=8cm]{scatter_chronology_baseline10_dbsamesample10_5_3.png}
	\end{center}
\end{figure}
